---
title: "R data.table"
output:
  html_document: default
  html_notebook: default
---

Description: Fast aggregation of large data (e.g. 100GB in RAM), fast ordered joins, fast add/modify/delete of columns by group using no copies at all, list columns, a fast friendly file reader and parallel file writer. Offers a natural and flexible syntax, for faster development.

```{r}
#create a huge dataset
set.seed(1234)
x1<-1:10000000
x2<-rnorm(10000000)
x3<-rt(10000000,2)
x4<-rf(10000000,2,3)
x5<-rpois(10000000,5)
x6<-sample(letters,10000000,replace = TRUE)
x7<-rchisq(10000000,3)
my.df<-data.frame(x1=x1,x2=x2,x3=x3,
                  x4=x4,x5=x5,x6=x6,
                  x7=x7)
write.csv(my.df,'test.csv',row.names = FALSE)
```

```{r}
#compare function read.table() and read.csv() of rbase and function fread() of package data.table.
filepath<-file.choose()
system.time(read.table(file=filepath,head=TRUE,sep = ','))
system.time(read.csv(file=filepath,head=TRUE,sep = ','))
library(data.table)
system.time(fread(input = filepath))
```

从中可以看出，fread()函数在读取大文本文件时，速度上有显著的提升，要比read.table()快了近7倍，比read.csv()也快了近4倍。

```{r}
#duplicated returns a logical vector indicating which rows of a data.table are duplicates of a row with smaller subscripts.
#unique returns a data.table with duplicated rows removed, by columns specified in by argument. When no by then duplicated rows by all columns are removed.
#example：remove duplicated data between col x5 and col x6 of dataset my.df
df<-my.df
dt<-data.table(my.df)
library(sqldf)
system.time(sqldf('select distinct x5,x6 from df'))
library(data.table)
system.time(unique(dt[,list(x5,x6)], by = c('x5','x6')))
```
同样的排重目的，read.table包中的unique函数比SQL快了100多倍！

```{r}
#function subset Returns subsets of a data.table.
system.time(subset(x = df, x2 >= 1 & x3 <= 0.5 & x6 == 'c' | x7 > 1.2))
system.time(subset(x = dt, x2 >= 1 & x3 <= 0.5 & x6 == 'c' | x7 > 1.2))
```
对1000W行的数据集，差异虽然不是很明显，但如果有更大的数据集的话，这种差异一定会显得非常明显。

```{r}
#setorder (and setorderv) reorders the rows of a data.table based on the columns (and column order) provided. It reorders the table by reference and is therefore very memory efficient.
library(plyr)
system.time(arrange(df, x2, desc(x3), x6))
library(data.table)
system.time(setorder(dt, x2, x3,x6))
```
通过使用plyr包中的arrange()函数和data.table包中的setorder()函数对比，发现后者比前者的速度快了130倍！

```{r}
#Grouping calculation
library(sqldf)
system.time(sqldf('select x6, avg(x1) A, min(x2) B,max(x3) C ,max(x5)-min(x5) D from df group by x6'))
library(data.table)
system.time(dt[, list(A = mean(x1), B = min(x2), C = max(x3), D = diff(range(x5))), by = x6])
```
为达到同样的聚合效果，data.table包所显示的速度是另一种方法的74倍！

通过以上几个案例的对比分析，我们可以看见read.table包中的函数应用比较简单（代码较少）而且运行速度也是非常快速的。除此之外，该包中还包括重命名变量名函数setnames()、数据整形函数melt()和dcast()、数据合并函数merge()和rbind()、rbindlist()等。详细信息可以查看相应的帮助文件。